---
title: "Team.rmd"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
choco <- read.csv("https://raw.githubusercontent.com/xdaiISU/ds202materials/master/hwlabs/data/choco.csv") 
str(choco)
```

Question 1

```{r}
ratings <- choco$Rating
hist(ratings)
```

There are a few outliers on the lower end between 1 and 2

```{r}
boxplot(ratings)
```

The box plot reveals the same thing, that there are outliers on the lower scale between and including 1 and 2

Question 2

```{r}
loc <- table(choco$Location)
loc2 <- sort(loc, decreasing = TRUE)
barplot(loc2)
```

Question 5

My first analysis will be comparing the date that chocolate was produced in comparison to it's rating. I will look at in 5 sections, 2006, 2009, 2012, 2015, and 2018.

```{r}
years <- choco$Date
unique(sort(years, decreasing = TRUE))
```

```{r}
inc1 <- choco[years == 2006,]
inc2 <- choco[years == 2009,]
inc3 <- choco[years == 2012,]
inc4 <- choco[years == 2015,]
inc5 <- choco[years == 2018,]

summary(inc1$Rating)
summary(inc2$Rating)
summary(inc3$Rating)
summary(inc4$Rating)
summary(inc5$Rating)
```

Through the summaries above, we can see that the lowest chocolate ratings have increased over time, as well as the mean ratings per year has shown an overall positive trend. From this, we can conclude that chocolate ratings have gone up overall over the course of the years.
